---
title: "R Notebook"
output: html_notebook
---

loading libraries
```{r}
library(tidyverse)
library(modelr)
library(ggfortify)
```



loading in the data
```{r}
project <- read_csv("project_management.csv")

```


```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_text(label = project$X1, hjust = -0.5)
```

outliers eyeballed from this graph:
influential: 5
non-influential: maybe 18, maybe 24

```{r}

proj_model <- lm(formula = actual_length ~ estimated_length, data = project)

```



```{r}
autoplot(proj_model, which = 5)
```

There aren't any Cook's distance lines in this plot. Plotting a Cook's Distance plot to check which outliers are influential

```{r}
autoplot(proj_model, which = 4)
```

clearly 5 is a massively influential outlier. 18 and 31 are influential outliers too, but not much. 


obtaining the intercept and regression coefficient of estimated_length for a model fitted to data ommiting point 24 (non influential outlier)
```{r}
model_non_influential_data <- project %>% 
  filter(X1 != 24)


model_non_influential <- lm(formula = actual_length ~ estimated_length, data = model_non_influential_data)
```

now plotting the data points, and both regressions obtained so far. 

```{r}
project %>% 
  add_predictions(proj_model) %>%
  mutate(pred_all = pred) %>% 
  add_predictions(model_non_influential) %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred_all), colour = "red") +
  geom_line(aes(y = pred), colour = "blue")
```

the intercept and regression coefficient of the two models are not that different at all. I'd stand by the point that point 24 is non influential.

```{r}
project %>% 
  add_predictions(model_non_influential) %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), colour = "blue")
```

```{r}
autoplot(proj_model)
```

thte Residuals vs Fitted plot os mostly centred around 0. It has a slight downward slope towards the right. It's mostly pretty alright, but pointg number 5 is an obvious outlier, and potentially a problem. Point 18 is also an outlier, that might be influential.

the normal q-q plot shows that the residuals are mostly normally distributed, with the exceptions of 5 (it's always 5 causing problems), and 18.

the Scale-Location plot is also okay, because it's not showing a trend in either direction.