---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(tsibble)
library(tsibbledata)
library(feasts)


date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")
```


```{r}
library(nycflights13)

```


1. 
```{r}
year(date1)
month(date1, label = TRUE, abbr = FALSE)
mday(date1)
yday(date1)
wday(date1)
```
2.
```{r}
next_fortnight <- weeks(2) + date1
previous_decade <- date2 - years(10)
```

3.
```{r}
this_year <- as_date(today())

interval_years <- lubridate::interval(previous_decade, this_year)
```

4. 
```{r}
nyc_date1 <- with_tz(date1, tzone = "America/New_York")
nyc_date2 <- with_tz(date2, tzone = "America/New_York")
```


5. 
```{r}
flights %>% 
  mutate(departure_date = make_datetime(year, month, day, hour, minute))
```

time series familiarity

6. 
```{r}
weather_tidy <- weather %>% 
  select(origin, time_hour, temp, humid, precip)
```
The time series is hourly. It starts on 2013-01-01, and there are 24 readings per day. The index variables in this case are time_hour, year, month, day, and hour. Having said that, there's nothing in time_hour that's not in the other columns, so I might get rid of those for conciseness sake.
The key in this data is the origin column. 

7. 
```{r}
weather_tsibble <- as_tsibble(weather_tidy, index = time_hour, key = origin)
```


8.
```{r}
weather_tsibble <- weather_tsibble %>% 
  mutate(year = year(time_hour), month = month(time_hour)) %>% 
  unite(month_year, c(year, month), sep = "-", remove = TRUE)

weather_tsibble %>% 
  ggplot(aes(x =time_hour, y = temp)) +
  geom_line(aes(colour = origin))
```
Plotting all of the data might not be the worst thing in the world, but there are just over twentysix thousand rows, which means just over 26000 data points. That's excessive. It might be easier to see if you did a graph of the average over a day. That would mean just over 1000 data points, rather than 26000. 

9.
```{r}
weather_rolling <- weather_tsibble %>% 
  group_by_key(origin) %>% 
  mutate(temp_ma = slide_dbl(temp, ~ mean(., na.rm = TRUE), .size = 720))

ggplot(weather_rolling) +
  geom_line(aes(x = time_hour, y = temp, group = origin), colour = "grey") +
  geom_line(aes(x = time_hour, y = temp_ma, colour = origin), size = 1) +
  facet_wrap(~ origin) +
  ylab("Temperature") +
  xlab("Time")
```


```{r}
class(weather_tsibble)
```



















