---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(beepr)
```

```{r}
code_clan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(code_clan_tweets)
names(code_clan_tweets)
```
```{r}
boxplot(code_clan_tweets$favorite_count)
```
There are outliers, but it's likely that a few tweets got more attention than others. For that reason, I'm not going to exclude the results and will perform all analysis on the whole dataset. 

```{r}
code_clan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(sum(favorite_count))
```

```{r}
code_clan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean(favorite_count))
```

```{r}
code_clan_tweets %>%
  mutate(media_type = replace_na(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(sum(favorite_count))
```

```{r}
code_clan_tweets_latin1 <- code_clan_tweets
Encoding(code_clan_tweets_latin1$text) <- "latin1"

code_clan_tweets_latin1 %>% 
  mutate(tweet_length = nchar(text)) %>% 
  summarise(mean(tweet_length))
```


```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")
```
I'm doing a left join here because I want to include all of the tweets, and all of the matching status URLs, I don't want to include a status URL for a tweet that isn't there. I'm also awware that both tibbles have the same number of rows. 
```{r}
code_clan_tweets_status <- left_join(code_clan_tweets, code_clan_info, by = "tweet_id")

code_clan_tweets_status <- code_clan_tweets_status %>% 
  select(tweet_id:status_url)
```

```{r}
codeclan_hashtags <- code_clan_tweets_status %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  filter(!is.na(hashtags))
```

```{r}

```




























