---
title: "R Notebook"
output: html_notebook
---

I'm creating the vector stock_prices.

```{r}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
```

I'm creating the vector day_of_week, containing each day twice

```{r}
day_of_week <- rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), times = 2)
day_of_week
```

creating a factorial vector called day_of_week_factor
```{r}
day_of_week_factor <- as.factor(day_of_week)
day_of_week_factor
```

creating a vector of stock prices which has names as days of the week
```{r}
named_stock_prices <- stock_prices
names(named_stock_prices) <- day_of_week
named_stock_prices
```

Making a dataframe called stock_data, containing the stock price and day of the week data
```{r}
stock_data <- data.frame(day_of_week, stock_prices)
View(stock_data)
```

Making a list called stock_list with named elements as follows: the vector of stock_prices, the vector day_of_week, and the data frame you made in question 3. Choose sensible names for the list elements.
```{r}
stock_list <- list("stock_prices" = stock_prices, "day_of_week" = day_of_week, "stock_data" = stock_data)
stock_list
```

Part two
I'm selecting the 4th, 5th, and 6th elements from stock_prices
```{r}
stock_prices[4:6]
```

I'm selecting all elements from stock_prices greater than 30
```{r}
stock_prices[stock_prices > 30]
```

I'm selecting the day of week column from the stock_data dataframe
```{r}
stock_data[, "day_of_week"]
```

I'm selecting the rows from stock_data where the stock_price value is less than 25
```{r}
stock_data[stock_prices < 25, ]
```

selecting the first column of stock_data
```{r}
stock_data[, 1]
```

selecting the third row of stock_data
```{r}
stock_data[3, ]
```

selecting the 3rd element from the first row of stock_data
```{r}
stock_data[3, 1]
```

selecting the dataframe from the stocks_list list
```{r}
stock_list["stock_data"]
```

