---
title: "R Notebook"
output: html_notebook
---

Here is a set of data on housing sale prices for the last few years in King County, near Seattle, between May 2014, and May 2015. 

First I'm going to tidy the data in a suitable way, so that it's ready for regression. 

```{r}
library(tidyverse)
library(GGally)
library(modelr)
```


```{r}
houses <- read_csv("data/kc_house_data.csv")

# selecting - id, because ID will be strongly correlated with price, for obvious reasons. Also removing date (unimportant), sqft_living15 (not interested in square footage of the nearest 15 houses), sqft_lot15, and zipcode (as long and lat will provide a better understanding of location)

houses <- houses %>% 
  select(-id, -date, -sqft_living15, -sqft_lot15, -zipcode)
```
```{r}
unique(houses$condition)
unique(houses$grade)
```

 converting yr_renovated and waterfront to logical variable for sake of simplicity.
 Converting condition to dummy variables. 
 
```{r}
houses_clean <- houses %>% 
  mutate(renovated = as.logical(yr_renovated),
         waterfront= as.logical(waterfront),
         condition_1 = ifelse(houses$condition == 1, 1, 0),
         condition_2 = ifelse(houses$condition == 2, 1, 0), 
         condition_3 = ifelse(houses$condition == 3, 1, 0),
         condition_4 = ifelse(houses$condition == 4, 1, 0)) %>% 
  select(-condition, -yr_renovated) %>% 
  mutate(grade_1 = ifelse(grade == 1, 1, 0),
         grade_3 = ifelse(grade == 3, 1, 0),
         grade_4 = ifelse(grade == 4, 1, 0),
         grade_5 = ifelse(grade == 5, 1, 0),
         grade_6 = ifelse(grade == 6, 1, 0),
         grade_7 = ifelse(grade == 7, 1, 0),
         grade_8 = ifelse(grade == 8, 1, 0),
         grade_9 = ifelse(grade == 9, 1, 0),
         grade_10 = ifelse(grade == 10, 1, 0),
         grade_11 = ifelse(grade == 11, 1, 0),
         grade_12 = ifelse(grade == 12, 1, 0)) %>% 
  select(-grade)
  
```


checking for aliased variables, then removing variables that lead to an alias
```{r}
alias(price ~ ., data = houses_clean)
```
From this, it looks like sqft_basement is strongly correlated with sqft_living and sqft_above. For this reason, I'll remove it from the data. 

```{r}
houses_clean <- houses_clean %>% 
  select(-sqft_basement)
```

I'm now going to systematically build a regression model containing up to four main effects. I'll test the regression diagnostics as I go. 

```{r}
houses_numeric <- houses_clean %>% 
  select(price:floors, view:long)

houses_logical <- houses_clean %>% 
  select(price, waterfront, renovated:grade_12)
```

```{r fig.height=7.5, fig.width=10}
ggpairs(houses_numeric)


beepr::beep(9)
```
This first plot shows that Price has the highest correlation with sqft_living at 0.702, followed by sqft_above at 0.606. 


```{r fig.height=11.25, fig.width=15}
ggpairs(houses_logical)

beepr::beep(9)
```

On this graph, the highest correlation with price is with grade_11 at 0.357, although it also appears there's some sort of correlation between waterfront and price.

Based on these graphs, I'm going to choose to make my first model with price~sqft_living, followed by price~sqft_above. 


```{r}
mod1a <- lm(price ~ sqft_living, data = houses_clean)
mod1b <- lm(price ~ sqft_above, data = houses_clean)

summary(mod1a)
summary(mod1b)
```

In both of these models, the p values for the coefficients and intercepts are <2e-16, which is very small. The r2 value for mod1a is 0.4929, the r2 value for mod1b is 0.3667. mod1a is quite a lot higher, so we're going to take mod1a going forward. 

```{r}
par(mfrow = c(2, 2))
plot(mod1a)
```

```{r}
par(mfrow = c(2, 2))
plot(mod1b)
```


```{r fig.height=20, fig.width=27, warning=FALSE, message=FALSE}
price_remaining_resid <- houses_clean %>% 
  add_residuals(mod1a) %>% 
  select(-price, -sqft_living)

price_remaining_resid %>% 
  ggpairs()

beepr::beep(8)
```

based on this graph, I'm going to choose lat, view, and waterfront as my next models. 

```{r}
mod2a <- lm(price ~ sqft_living + view, data = houses_clean)
mod2b <- lm(price ~ sqft_living + lat, data = houses_clean)
mod2c <- lm(price ~ sqft_living + waterfront, data = houses_clean)

summary(mod2a)
summary(mod2b)
summary(mod2c)
```
From these models, mod2b has the highest r2 value at 0.566. It also has a p value of 2e-16 for both coefficientsa and the y intercept, which 2a and 2c don't. In addition, it also has the highest adjusted r2 value. I'll be using mod2b from here on. 

```{r}
par(mfrow = c(2, 2))
plot(mod2a)
```


```{r}
par(mfrow = c(2, 2))
plot(mod2b)
```

```{r}
par(mfrow = c(2, 2))
plot(mod2c)
```


```{r}
price_remaining_resid <- houses_clean %>% 
  add_residuals(mod1a) %>% 
  select(-price, -sqft_living, -lat)

houses_numeric_resid <- price_remaining_resid %>% 
  select(bedrooms:floors, view:long, resid)

houses_logical_resid <- price_remaining_resid %>% 
  select(waterfront, renovated:grade_12, resid)

houses_numeric_resid %>% 
  ggpairs()


beepr::beep(8)
```

```{r fig.height=20, fig.width=27, warning=FALSE, message=FALSE}

houses_logical_resid %>% 
  ggpairs()

beepr::beep(8)
```

based on these two graphs, I'm going to run 3 different model 3s. mod3a view, mod3b yr_built, mod3c waterfront. 

```{r}
mod3a <- lm(price ~ sqft_living + lat + view, data = houses_clean)
mod3b <- lm(price ~ sqft_living + lat + yr_built, data = houses_clean)
mod3c <- lm(price ~ sqft_living + lat + waterfront, data = houses_clean)

summary(mod2a)
summary(mod2b)
```

