---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
drinks_content <- read_csv("data/starbucks_drinkMenu_expanded.csv")
```

```{r}
head(drinks_content)
tail(drinks_content)
```

```{r}
dim(drinks_content)
```
Calculating summary statistics to check the mean, the variance, and the normality of the Calories variable. 

Question 3
```{r}
summary(drinks_content$Calories)
```
mean of the Calories variable is 193.9, and the median is 185.0. Considering the quartiles, this is not extremely far off. 
```{r}
var(drinks_content$Calories)
```
The variance of the Calories variable is 10580.86. This is *huge*.

I'm not sure what the normality means, and google is not being helpful. 


Checking if there are any outliers in the Calories variable by creating a boxplot.

```{r}
calories_boxplot <- boxplot(drinks_content$Calories)
```
There is one outlier in the Calories data.

Getting the actual values of the outlier

```{r}
outliers <- boxplot(drinks_content$Calories, plot = FALSE)$out
drinks_content[which(drinks_content$Calories %in% outliers), ]
```

I'm removing the outlier from the data for a few reasons. The first is that there is only one. It's more likely to be a true outlier if there is only one, rather than if there are lots, when it is more justified to interpret it as a trend. The second reason is that the difference between the outlier and the next highest value is more than 10% of the next highest value. Removing the outlier would significantly affect the variance. And finally, the data is already skewed, as the upper whisker is longer than the lower. Including the outlier will only increase that. 

```{r}
drinks_content_no_outlier <- drinks_content[-which(drinks_content$Calories %in% outliers), ]

```
I removed the outlier in a similar way to how I selected it, only adding a - sign, which removes the selection from the tibble.
```{r}
var(drinks_content_no_outlier$Calories)
```
```{r}
boxplot(drinks_content_no_outlier$Calories)
```
Selecting the variables beverage_category, beverage, beverage prep and calories from the data. 
Also checking for NA values in the calories variable, and dropping any that show up.
```{r}
filter(drinks_content_no_outlier, is.na(Calories))
```

```{r}
clean_drinks_content <- drinks_content_no_outlier %>%
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
  drop_na(Calories) 
```
filtering the data so that we only see classic espresso drinks

```{r}
clean_drinks_content_classic_espresso <- clean_drinks_content %>%
  filter(Beverage_category == "Classic Espresso Drinks")
```

```{r}
drink_calories <- clean_drinks_content_classic_espresso %>%
  mutate(calorie_diff = 135 - Calories)
  
```

```{r}
drinks_grouped <- clean_drinks_content_classic_espresso %>%
  group_by(Beverage_prep) %>%
  summarise(mean_cal = mean(Calories)) %>%
  arrange(desc(mean_cal))
drinks_grouped
  
```
now doing the last ~4 parts in one pipe
```{r}
drinks_grouped <- drinks_content_no_outlier %>%
  select(Beverage, Beverage_category, Beverage_prep, Calories) %>%
  filter(Beverage_category == "Classic Espresso Drinks") %>%
  mutate(calorie_diff = 135 - Calories) %>%
  group_by(Beverage_prep) %>%
  summarise(mean_cal = mean(Calories)) %>%
  arrange(desc(mean_cal))
drinks_grouped
```

```{r}
filter(drink_calories, Calories == max(Calories) | Calories == min(Calories))
```
The caffe mocha without whipped cream is the classic esspresso drink with the most calories. There are two that have the least, Caffe Americano and Espresso.


```{r}
above_average_calories <- drinks_grouped %>%
  filter(Calories > mean(Calories))
above_average_calories
```


Using 
```{r}
drinks_distribution <- drinks_grouped %>%
  filter(cume_dist(desc(Calories)) < 0.25)
drinks_distribution
```




























