---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
drinks_content <- read_csv("data/starbucks_drinkMenu_expanded.csv")
```

```{r}
head(drinks_content)
tail(drinks_content)
```

```{r}
dim(drinks_content)
```
Calculating summary statistics to check the mean, the variance, and the normality of the Calories variable. 

Question 3
```{r}
summary(drinks_content$Calories)
```
mean of the Calories variable is 193.9, and the median is 185.0. Considering the quartiles, this is not extremely far off. 
```{r}
var(drinks_content$Calories)
```
The variance of the Calories variable is 10580.86. This is *huge*.

I'm not sure what the normality means, and google is not being helpful. 


Checking if there are any outliers in the Calories variable by creating a boxplot.

```{r}
calories_boxplot <- boxplot(drinks_content$Calories)
```
There is one outlier in the Calories data.

Getting the actual values of the outlier

```{r}
outliers <- boxplot(drinks_content$Calories, plot = FALSE)$out
drinks_content[which(drinks_content$Calories %in% outliers), ]
```

I'm removing the outlier from the data for a few reasons. The first is that there is only one. It's more likely to be a true outlier if there is only one, rather than if there are lots, when it is more justified to interpret it as a trend. The second reason is that the difference between the outlier and the next highest value is more than 10% of the next highest value. Removing the outlier would significantly affect the variance. 

```{r}
drinks_content_clean <- drinks_content[-which(drinks_content$Calories %in% outliers), ]
drinks_content_clean

```















