---
title: "R Notebook"
output: html_notebook
---
1. 
```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
dim(backpack)
head(backpack)
```

2.
```{r}
backpack %>% 
  ggplot() +
  geom_boxplot(aes(y = backpack_weight)) +
  labs(
    y = "Backpack Weight", 
    title = "Boxplot of Backpack Weights"
  )
```
This boxplot shows that most of the backpacks have a weight between ~20 and ~2. There are three outliers, and 50% of the weights are between 7 and 14 weight units (these are unspecified in the data)

3.
```{r}
backpack %>% 
  ggplot() +
  geom_boxplot(aes(x = sex, y = backpack_weight, colour = sex))
```
This boxplot, split by gender, shows that there is a greater variation in the males backpacks. The median and upper quartile are both greater for males than females, as well as the maximum value. The minimum and lower quartile, however, are the same. 

4. 
```{r}
backpack %>% 
  ggplot() +
  geom_point(aes(x = body_weight, y = backpack_weight)) +
  labs(
    x = "Body Weight", 
    y = "Backpack Weight", 
    title = "Graph Showing Body Weight vs Backpack Weight"
  )
```
There doesn't appear to be much relationship between body weight and backpack weight in this data set. At a stretch, you could maybe claim that there's a positive correlation, but there would be a LOT of outliers, and it's a VERY loose relationship.

5. 
```{r}
backpack %>% 
  ggplot() +
  geom_point(aes(x = body_weight, y = backpack_weight, colour = sex, shape = sex)) +
  labs(
    x = "Body Weight", 
    y = "Backpack Weight", 
    title = "Graph Showing Body Weight vs Backpack Weight for Male and Female"
  )
```
This plot shows clearly that males tend to weigh more than females, and whilst the difference isn't as clear, their backpacks do tend to weigh more. There doesn't appear to be any more of a correlation for males or females, however. 

6 & 7.
```{r}
backpack %>%
  mutate(back_problems = as.logical(back_problems)) %>% 
  ggplot() +
  geom_bar(aes(x = back_problems, fill = sex)) +
  labs(
    x = "Back Problems",
    y = "Number of Students",
    title = "Number of Students With and Without Back Problems",
    fill = "Sex"
  )
```

I couldn't work out a better way to show the proportion. I wanted to have it in one bar, so that you could see how it's make up, but I couldn't work out how to do that. In any case, this does give an idea of the proportions of students with back problems. You can see that about 31 of the students do have back problems, and about 64 do not, giving a ration of about 1/3 of students with back problems. This proportion is ver different between males and females, however, with just under 50% of females having back problems, but only ~17% of males having back problems.

8. 
```{r}
backpack %>% 
  mutate(back_problems = as.logical(back_problems)) %>% 
  ggplot(aes(x = backpack_weight, y = body_weight)) +
  geom_point(aes(colour = sex)) +
  facet_wrap(sex ~ back_problems, labeller = "label_both") +
  labs(
    x = "Backpack Weight", 
    y = "Body Weight",
    colour = "Sex"
  )
```









































```{r}
```

