---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readxl)
library(janitor)
library(GGally)
library(beepr)
library(tidyverse)
library(pROC)
library(modelr)
library(caret)
library(broom)
```


ALPHA VALUE TO REJECT NULL HYPOTHESES = 0.05

```{r}
telecoms_churn <- read_excel("telecomms_churn.xlsx")

glimpse(telecoms_churn)
```
```{r}
unique(telecoms_churn$Contract)
unique(telecoms_churn$SeniorCitizen)
unique(telecoms_churn$InternetService)
```


1.
```{r}
telecoms_clean <- telecoms_churn %>% 
  clean_names() %>% 
  mutate(churn = ifelse(churn == "No", FALSE, TRUE),
         partner = ifelse(partner == "No", FALSE, TRUE),
         dependents = ifelse(dependents == "No", FALSE, TRUE),
         phone_service = ifelse(phone_service == "No", FALSE, TRUE),
         senior_citizen = ifelse(senior_citizen == 0, FALSE, TRUE)) %>% 
  select(-customer_id) %>% 
  mutate(contract = as.factor(contract),
         internet_service = as.factor(internet_service))
  
  

```

```{r fig.height=12, fig.width=15, message=FALSE, warning=FALSE}
ggpairs(telecoms_clean)
beep(1)
```

3. 
Creating three seperate single predictor logistic regression models. 
The three most promising predictors in the ggpairs graph were senior_citizen, tenure, and phone service.
```{r}
telecom_mod1a <- glm(churn ~ senior_citizen, 
                     data = telecoms_clean,
                     family = binomial(link = "logit"))

telecom_mod1b <- glm(churn ~ tenure,
                     data = telecoms_clean,
                     family = binomial(link = "logit"))

telecom_mod1c <- glm(churn ~ phone_service,
                     data = telecoms_clean, 
                     family = binomial(link = "logit"))
```

checking to see whether the coefficients of the models are statistically significant. 

```{r}
summary(telecom_mod1a)
```
p value of coefficient is <2e-16. This is lower than alpha, and we can reject the null hypothesis. Coefficient is statistically significant. 

```{r}
summary(telecom_mod1b)
```
p value of coefficient is <2e-16. This is lower than alpha, and we can reject the null hypothesis. Coefficient is statistically significant.

```{r}
summary(telecom_mod1c)
```
p value of coefficient is 0.316. This is higher than alpha, and we can't reject the null hypothesis. Coefficient is not statistically significant.

Making another single predictor model using contract
```{r}
telecom_mod1d <- glm(churn ~ contract,
                     data = telecoms_clean, 
                     family = binomial(link = "logit"))
summary(telecom_mod1d)
```
p values of coefficients are both <2e-16. This is lower than alpha, and we can reject the null hypothesis. Coefficients are statistically significant.


4. 

plotting a ROC curve for each of the classifiers. Going to put them all on same axes. 

```{r}
telecom_1a_pred <- telecoms_clean %>% 
  add_predictions(telecom_mod1a, type = "response")

roc_object1a <- telecom_1a_pred %>% 
  roc(response = churn, predictor = pred)


telecom_1b_pred <- telecoms_clean %>% 
  add_predictions(telecom_mod1b, type = "response")

roc_object1b <- telecom_1b_pred %>% 
  roc(response = churn, predictor = pred)


telecom_1d_pred <- telecoms_clean %>% 
  add_predictions(telecom_mod1d, type = "response")

roc_object1d <- telecom_1d_pred %>% 
  roc(response = churn, predictor = pred)



roc_curve <- ggroc(data = list("1a" = roc_object1a, "1b" = roc_object1b, "1d" = roc_object1d), legacy.axes = TRUE) +
  coord_fixed()
roc_curve
```

Eugh.... 1a is baaad... 1b and 1d are eh

Let's look at AUC values
```{r}
auc_1a <- auc(roc_object1a)
auc_1b <- auc(roc_object1b)
auc_1d <- auc(roc_object1d)

auc_1a
auc_1b
auc_1d
```
The AUC value is highest for mod1b, but mod1d is pretty similar. mod1a is barely better than random. 

5. 
Performing cross validation to check how representative the AUC values calculated above will be for unseen data. 
```{r}
#making the churn and senior_citizen columns factors, so that they're compatibe with caret package. 
telecoms_cleaner <- telecoms_clean %>% 
  mutate(churn = as_factor(ifelse(churn, "t", "f"))) %>% 
  mutate(senior_citizen = as_factor(ifelse(senior_citizen, "t", "f")))

train_control <- trainControl(method = "repeatedcv", 
                              number = 10,
                              repeats = 100, 
                              savePredictions = TRUE,
                              classProbs = TRUE,
                              summaryFunction = twoClassSummary)

model1a <- train(churn ~ senior_citizen, 
                 data = telecoms_cleaner,
                 trControl = train_control,
                 method = "glm",
                 family = binomial(link = "logit"))

model1b <- train(churn ~ tenure, 
                 data = telecoms_cleaner,
                 trControl = train_control,
                 method = "glm",
                 family = binomial(link = "logit"))

model1d <- train(churn ~ contract, 
                 data = telecoms_cleaner,
                 trControl = train_control,
                 method = "glm",
                 family = binomial(link = "logit"))
```
```{r}
summary(model1a)
model1a$results
```
AUC value (labelled as ROC) is 0.563. Barely better than a random guess

```{r}
summary(model1b)
model1b$results
```
AUC value is 0.740

```{r}
summary(model1d)
model1d$results
```

AUC value is 0.739. Barely, but just lower than model1b. 

6.
Taking model1b, and interpreting the fitted coefficient of contract. 

```{r}
odds_at_32 <- tibble(tenure = 32) %>% 
  add_predictions(telecom_mod1b, type = "response") %>% 
  mutate(odds = pred / (1 - pred)) %>% 
  select(odds)
odds_at_32
```
with a tenure of 32 years, the odds of a customer churning are about 1 to 3.  

lets see what the odds factor is for a change of -20 years, and a tenure of 12 years
```{r}
b_tenure <- tidy(telecom_mod1b) %>% 
  filter(term != "(Intercept)") %>% 
  select(estimate)

odds_factor <- exp(b_tenure * -20)
```
That's an odds factor of 2.17
```{r}
odds_at_12 <- odds_factor * odds_at_32
```
That's an odds of about 2 to 3. Which means that a customer is twice as likely to churn if they've had a tenure of 12 years. 

```{r}
unique(telecoms_clean$contract)
```


Now, looking at model1d, which was the best model. 
```{r}
b_contract_1year <- tidy(telecom_mod1d) %>% 
  filter(term == "contractOne year") %>% 
  select(estimate)

odds_ratio_1_year <- exp(b_contract_1year)

b_contract_2year <- tidy(telecom_mod1d) %>% 
  filter(term == "contractTwo year") %>% 
  select(estimate)

odds_ratio_2_year <- exp(b_contract_2year)

odds_ratio_1_year
odds_ratio_2_year
```

