---
title: "R Notebook"
output: html_notebook
---
```{r}
library(prob)
library(gtools)
library(tidyverse)
```

1.
p(d6 <5) = 2/3

2. 
216

3. 
i. 
```{r}
roll_4 <- rolldie(4) 

total_5_6_7 <- roll_4 %>% 
  mutate(sum = X1 + X2 + X3 + X4) %>% 
  filter(sum == 5 | sum == 6 | sum == 7)
```

ii.
```{r}
p_total_5_6_7 <- nrow(total_5_6_7) / nrow(roll_4)
p_total_5_6_7
```

iii.
in answering iii, we assume first, that the question is meant to ask about part ii.
secondly, we assume that the outcomes of the subsequent rolls don't depend on the first roll.

4. 
```{r}
people <- 1:5

order_of_people <- as_tibble(permutations(n = 5,
                                          r = 5, 
                                          v = people,
                                          repeats.allowed = FALSE))


probability_ordered_left_to_right <- 1/nrow(order_of_people)
```

5. 
i. 
```{r}
1 / nrow(rolldie(6))
```
ii.
```{r}
numbers <- 1:6
nrow(as_tibble(permutations(n = 6, r = 6, v = numbers, repeats.allowed = FALSE))) / nrow(rolldie(6))
```

6. 
0.5

7. 
i.
```{r}
patients <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry")
nrow(as_tibble(permutations(n = length(patients), r = 5, v = patients, repeats.allowed = FALSE)))
```
ii.
```{r}
as_tibble(permutations(n = length(patients), r = 5, v = patients, repeats.allowed = FALSE)) %>% 
  filter(isin(., c("Gianna", "Dinesh"), ordered = FALSE))

2400/6720
```
iii.
```{r}
as_tibble(permutations(n = length(patients), r = 5, v = patients, repeats.allowed = FALSE)) %>% 
  filter(isin(., c("Gianna", "Dinesh"), ordered = TRUE))
1200/6720
```
iv.
```{r}
nrow(as_tibble(permutations(n = length(patients), r = 5, v = patients, repeats.allowed = FALSE)) %>% 
  filter((V1 == "Carmen" & V2 == "Henry") | (V1 == "Henry" & V2 == "Carmen")))

```

8.
```{r}
students <- 1:8
nrow(as_tibble(combinations(n = 8, r = 5, v = students, repeats.allowed = FALSE)))
as_tibble(permutations(n = 8, r = 5, v = students, repeats.allowed = FALSE))
```

9. 
```{r}

```


































